\setcounter{section}{5}
\section{The Riemann-Stieltjes Integral}

\begin{theorem}[Riemann Integrability]
  $ f\colon [a, b] \to \mathbb{R} $ is Riemann integrable if 
  \begin{flalign*}
    \overline{ \int_{a}^{b} } f\,dx = 
    \underline{ \int_{a}^{b} } f\,dx.
  \end{flalign*}
\end{theorem}

\setcounter{theorem}{3}
\begin{theorem}[Refinement Improves Integral]
  If $ P^* $ refines $ P $, then
  \begin{flalign*}
    L(P, f, \alpha) \leq L(P^*, f, \alpha) \leq U(P^*, f, \alpha) \leq U(P, f, \alpha).
  \end{flalign*}
\end{theorem}

\begin{theorem}[Upper RS Integral Bounds Lower RS Integral]
  \begin{flalign*}
    \underline{ \int_{a}^{b} } f\,d\alpha
    \leq \overline{ \int_{a}^{b} } f\,d\alpha.
  \end{flalign*}
\end{theorem}

\begin{theorem}[Characterization of RS Integrability]
  The following are equivalent:
  \begin{enumerate}
    \item $ f \in \mathcal{R}_{\alpha}[a, b] $,
    \item $ \forall \varepsilon > 0 $ $ \exists P_{\varepsilon} $ such that 
      $ U(P, f, \alpha) - L(P, f, \alpha) < \epsilon $.
  \end{enumerate}
\end{theorem}

\setcounter{theorem}{7}
\begin{theorem}[Continuous $ f $ Entails Integrability]
  Suppose
  \begin{enumerate}
    \item $ f\colon [a, b] \to \mathbb{R} \in \mathcal{C}_0[a, b]$,
    \item  $ \alpha\colon [a, b] \to \mathbb{R} $ is monotonically increasing.
  \end{enumerate}
  Then $ f \in \mathcal{R}_{\alpha}[a, b] $.
\end{theorem}

\begin{theorem}[Continuous $ \alpha $ Entails Integrability]
  Suppose 
  \begin{enumerate}
    \item $ f $ is monotonically increasing.
    \item $ \alpha \in \mathcal{C}_0[a, b]$,
  \end{enumerate}
  Then $ f \in \mathcal{R}_{\alpha}[a, b] $.
\end{theorem}

\begin{theorem}[Continuous $ f $ or  $ \alpha $ Entails Integrability]
  Let $ S = \{s_1, \cdots, s_k\} \subset [a, b] $ be finitely many points.
  \begin{enumerate}
    \item $ f $ is continuous except for at $ s_i \in S $.
    \item $ \alpha $ is monotonically increasing, and continuous at each $ s_i $.
  \end{enumerate}
  Then $ f \in \mathcal{R}_{\alpha}[a, b] $.
\end{theorem}

\newpage

\begin{theorem}[Continuous Mapping On Function Preserves Integrability]
  Suppose
  \begin{enumerate}
    \item $ f \in \mathcal{R}_{\alpha}[a, b] $,
    \item $ m \leq f(x) \leq M $ for $ a \leq x \leq b $,
    \item $ \phi\colon[m, M] \to \mathbb{R} \in \mathcal{C}_0 $,
  \end{enumerate}
  Then $ \phi \circ f \in \mathcal{R}_{\alpha}[a, b] $.
\end{theorem}

\begin{theorem}[Linearity and Related Properties]
  Suppose $ f, f_1, f_2 \in \mathcal{R}_{\alpha}[a, b] $.
  \begin{enumerate}
    \item Linearity of $ f $.
      \begin{enumerate}
        \item $ f_1 + f_2 \in \mathcal{R}_{\alpha}[a, b] $. 
        \item $ cf \in \mathcal{R}_{\alpha}[a, b] $ (for $ c \in \mathcal{R} $). 
      \end{enumerate}
    \item Integral preserves order.
      \begin{itemize}
        \item If $ f_1 \leq f_2 $ on $ [a, b] $, then
          \begin{flalign*}
            \int_{a}^{b}f_1\,d\alpha
            \leq \int_{a}^{b}f_2\,d\alpha
          \end{flalign*}
      \end{itemize}
    \item Limits of integration can be split.
      \begin{itemize}
        \item $ f \in \mathcal{R}_{\alpha}[a, c] $ and $ f \in \mathcal{R}_{\alpha}[c, b] $.
          Particularly,
      \end{itemize}
      \begin{flalign*}
        \int_{a}^{b} f\, d\alpha = 
        \int_{a}^{c} f\,d\alpha
        + \int_{c}^{b} f\,d\alpha.
        \tag{Where $ c \in (a, b) $}
      \end{flalign*}
    \item Upper bound on integral.
      \begin{flalign*}
        \left| \int_{a}^{b}f\,d\alpha \right| \leq M(\alpha(b) - \alpha(a))
        \tag{Where $ M = \sup\{f(x)\colon a \leq x \leq b\} $}
      \end{flalign*}
    \item Linearity of $ \alpha $.
      \begin{itemize}
        \item Suppose $ f \in \mathcal{R}_{\alpha_1} $ and $ f \in \mathcal{R}_{\alpha_2} $.
        \item Then  $ f \in \mathcal{R}_{\alpha_1 + \alpha_2} $ and 
          \begin{flalign*}
            \int_{a}^{b} f\,d(\alpha_1 + \alpha_2) 
            = \int_{a}^{b} f\,d\alpha_1 + \int_{a}^{b} f\,d\alpha_2.
          \end{flalign*}
      \end{itemize}
  \end{enumerate}
\end{theorem}

\newpage

\begin{theorem}[Triangle inequality]
  For $ f \in \mathcal{R}_{\alpha}[a, b] $,
  \begin{flalign*}
    \left| \int_{a}^{b} f\, d\alpha \right|
    \leq \int_{a}^{b} |f|d\alpha.
  \end{flalign*}
\end{theorem}

\begin{theorem}[Product of two integrable functions is integrable]
  If $ f, g \in \mathcal{R}_{\alpha}[a, b] $, then $ fg \in \mathcal{R}_{\alpha}[a, b] $.
\end{theorem}

\begin{theorem}[Integrator step at continuous point extracts value]
  Suppose
  \begin{enumerate}
    \item $ f $ is bounded,
    \item $ f $ is continuous,
    \item  $ s \in (a, b) $,
    \item  $ \alpha(x) = I(x - s) $.
  \end{enumerate}
  Then,
  \begin{flalign*}
    \int_{a}^{b} f\,d\alpha = f(s).
  \end{flalign*}
\end{theorem}

\begin{theorem}[Infinite step integrator]
  Suppose
  \begin{enumerate}
    \item $ \displaystyle \alpha(x) = \sum_{i=1}^{ \infty } c_i I(x - s_i) $
      \begin{itemize}
        \item Where $ c_n \geq 0 $ such that  $ \sum_{i=1}^{ \infty } c_i < \infty $,
        \item and $ \{s_i\} $ are distinct points,
      \end{itemize}
    \item $ f $ is continuous.
  \end{enumerate}
  Then 
  \begin{flalign*}
    \int_{a}^{b} f\,d\alpha 
    = \sum_{i=1}^{\infty} c_i f(s_i).
  \end{flalign*}
\end{theorem}

\begin{theorem}[Explicit Form of Integrator]
  Suppose
  \begin{enumerate}
    \item $ \alpha \in C_1[a, b]$ and monotone. 
    \item $ \alpha' \in \mathcal{R}_{\alpha}[a, b] $.
  \end{enumerate}
  Then,
  \begin{flalign*}
    \int_{a}^{b}f\,d\alpha
    = \int_{a}^{b} f(x)\alpha'(x) dx
  \end{flalign*}
\end{theorem}

\newpage
\setcounter{theorem}{18}
\begin{theorem}[Change of Variables]
  Suppose
  \begin{enumerate}
    \item $ \phi $ is 
      \begin{enumerate}
        \item Strictly increasing on $ [a, b] $,
        \item Continuous on $ [a, b] $,
        \item Onto on  $ [a, b] $.
      \end{enumerate}
    \item $ f \in \mathcal{R}_{\alpha}[a, b] $.
  \end{enumerate}
  Then,
  \begin{flalign*}
    \int_{a}^{b}f\,d\alpha
    = \int_{\phi^{-1}(a)}^{\phi^{-1}(b)} (f\circ\phi)\, d(\alpha\circ\phi).
  \end{flalign*}
\end{theorem}

\begin{theorem}[Continuity and Differentiability of Antiderivative]
  Let $ f \in \mathcal{R}_{\alpha}[a, b] $ with  $ x \in [a, b] $.
  If we define 
  \begin{flalign*}
    F(x) = \int_{a}^{x} f(t)dt,
  \end{flalign*}
  then
  \begin{enumerate}
    \item $ F $ is continuous on $ [a, b] $,
    \item For $ x_0 $ where $ f $ is continuous at $ x_0 $,
      $ F'(x_0) = f(x_0) $.
  \end{enumerate}
\end{theorem}

\begin{theorem}[Fundamental Theorem of Calculus]
  If there exists $ F $ such that:
  \begin{enumerate}
    \item $ F $ is differentiable on  $ [a, b] $
    \item $ F' = f $,
  \end{enumerate}
  \begin{flalign*}
    F(b) - F(a) = \int_{a}^{b} f(x) dx
  \end{flalign*}
\end{theorem}

\begin{theorem}[Integration By Parts]
  For differentiable $ F, G $ such that $ F' = f $ and  $ G' = g $,
  \begin{flalign*}
    \int_{a}^{b} F(x)g(x) dx
    &= F(b)G(b) - F(a)G(a) - \int_{a}^{b} f(x)G(x) dx.
  \end{flalign*}
\end{theorem}
