\section{Power Series}

\begin{theorem}[Convergent power series converges uniformly]
  If $ f(x) = \sum c_n x^n $ converges on $ |x| < R $,
  then $ f_n\colon [-R + \varepsilon, R - \varepsilon] $ converges uniformly 
  $ \forall \varepsilon > 0 $ (partial sum).

  Furthermore, the derivative is well-defined for $ |x| < R $,
  \begin{flalign*}
    f'(x) = \sum nc_n x^{n - 1}.
  \end{flalign*}
\end{theorem}

\begin{theorem}[Abel's Theorem]
  Suppose  
  \begin{enumerate}
    \item $ \sum c_n $ converges,
    \item $ f(x) = \sum c_n x^n $ has radius of convergence $ 1 $.
  \end{enumerate}

  Then 
  \begin{flalign*}
    \lim_{x\to 1^-} f(x) = \sum c_n.
  \end{flalign*}

  (Consistent behavior as we approach radius of convergence).
\end{theorem}

\begin{theorem}[Interchange of summation order]
  If 
  \begin{flalign*}
    \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} \left| a_{ij} \right| < \infty,
  \end{flalign*}

  then 
  \begin{flalign*}
    \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} a_{ij}
    = \sum_{j=1}^{\infty} \sum_{i=1}^{\infty} a_{ij}.
  \end{flalign*}
\end{theorem}

\begin{theorem}[Taylor Series]
  If $ \sum c_n x^n $ converges on  $ \left| x \right| < R $,
  then $ \forall |a| < R $,
  \begin{flalign*}
    f(x) = \sum_{i=0}^{\infty} \frac{f^{(n)}(a)}{n!}(x - a)^n
  \end{flalign*}

  \textbf{at least} on $ |x - a| < R - |a| $.


  (We can center a Taylor series within the radius of convergence).
\end{theorem}

\begin{theorem}[Series on limiting sequence uniquely identifies sequence.]
  Let $ \sum a_n x^n $ and  $ \sum b_n x^n $ have the same radius of convergence
  $ \geq R $.
  Also suppose that $ D \subset (-R, R) $ has a limit point in  $ (-R, R) $.
  If  $ \sum a_n x^n = \sum b_n x^n $  $ \forall x\in D $,
  then $ a_n = b_n $.
\end{theorem}

\newpage

\setcounter{theorem}{7}
\begin{theorem}[Fundamental Theorem of Algebra]
  All complex polynomials have a root.
\end{theorem}

\setcounter{theorem}{10}

\begin{theorem}[Optimality of partial Fourier series coefficients]
  Suppose $ f \in \mathcal{R}[a, b] $ 
  and  $ \{\phi_n\} $ is orthonormal.
  Then let $ S_n = \sum_{m=1}^{n} c_m \phi_m $ 
  and let $ T_n = \sum_{m=1}^{n} a_m \phi_m $.
  Then
  \begin{flalign*}
    \|f - S_n\|_2 \leq \|f - T_n\|_2
  \end{flalign*}

  $ \forall n $. 
  Equality only holds if $ a_m = c_m $  $ \forall m $.
  Note this is w.r.t. L2 norm (defined with inner product),
  and not infinity norm.

  Corollaries:
  \begin{itemize}
    \item $ \|S_n\|_2^2 \leq \|f\|_2^2 $.
  \end{itemize}
\end{theorem}

\begin{theorem}[Changes in definition]
  Now 
  \begin{enumerate}
    \item We only consider functions $ f \colon [-\pi, \pi] \to \mathbb{C} $.
    \item $ \langle f, g \rangle = \frac{1}{2\pi} \int_{-\pi}^{\pi} f(x)\bar{g}(x)dx $.
  \end{enumerate}
\end{theorem}

\setcounter{theorem}{13}

\begin{theorem}[Lipchitz continuity implies convergence of Fourier series]
  Suppose $ x \in [-\pi, \pi] $,
  and $ f \colon [-\pi, \pi] \to \mathbb{C} $. 
  If $ \exists \delta, M > 0 $ s.t.
  \begin{flalign*}
    \left| f(x + t) - f(x) \right| \leq M|t|
  \end{flalign*}
  $ \forall |t| < \delta $,
  then
  \begin{flalign*}
    \lim_{N\to \infty} S_N(x) = f(x).
  \end{flalign*}
\end{theorem}

\begin{theorem}[Trig polynomial approximation]
  All $ 2\pi $-periodic continuous functions can be uniformly approximated by a trig polynomial.

  Let  $ f \colon \mathbb{R} \to \mathbb{C} $ be  $ 2\pi $-periodic.
  Then  $ \forall \varepsilon > 0 $,
  $ \exists $ a trig polynomial in the form
  \begin{flalign*}
    p_N(x) = \sum_{n=-N}^{N} a_n e^{inx}
  \end{flalign*}
  s.t. $ \|p_N - f\| < \varepsilon $.
  
\end{theorem}

\begin{theorem}[Convergence of Fourier series in L2]
  For $ f \in \mathcal{R}[-\pi, \pi] \to \mathbb{C} $,
  \begin{enumerate}
    \item $ \lim_{N\to \infty} \|f - S_N(f)\|_2 = 0 $.
    \item Parseval relation: $ \langle f, g \rangle = (c, \gamma) $.
      \begin{itemize}
        \item Bessel's inequality follows from this:
          $ \|f\|_2^2 = (c, c) = \sum_{n=-\infty}^{\infty} |c_n|^2 $.
      \end{itemize}
  \end{enumerate}
\end{theorem}
